A Review on Multi-Label Learning Algorithms

### 2018-01-13 Paper/Presentation/mll_review.tex
Update presentation

Multi-label supervised learning
\begin{itemize}
	\item Multiple labels per instance: $\{ (x_i, \bm{y}_i)\}, i = 1, \dots N, x \in X, \bm{y} \in \mathbb{P}(Y)$
	\item Learn a model $f: X \times Y \rightarrow r$ where $r\in \mathbb{R}$ is the confidence that $y_i$ characterizes $x_i$
	\item For classification, assume that $x_i$ belongs to $y_i$ if $r$ is greater than some threshold $t(x_i)$

@@

\begin{frame}
\frametitle{\insertsection : \insertsubsection}
Algorithms in two categories:
\begin{itemize}
	\item \emph{Problem Transformation Methods: }Transform the learning problem into other well-established learning scenarios (fit data to algorithm philosophy)
	\item \emph{Algorithm Adaptation Methods: }Adapt popular learning techniques to deal with multi-label data directly (fit algorithm to data philosophy)
\end{itemize}
\begin{figure}
	\begin{center}
		\includegraphics[scale = 0.25]{images/algorithmsclass.png}
		\caption{8 representative algorithms}
	\end{center}
\end{figure}
\end{frame}

@@

\begin{frame}
\frametitle{\insertsection : \insertsubsection}
\emph{Binary Relevance}
\begin{itemize}
	\item Decompose problem into q independent binary classification problems per possible label in the label space
\end{itemize}

>>>>

Multi-label supervised learning
\begin{itemize}
	\item Multiple labels per instance: $\{ (x_i, \bm{y}_i)\}, i = 1, \dots N, x \in X, \bm{y} \in \mathbb{P}(Y)$
	\item Learn a model $f: X \times Y \rightarrow r$ where $r\in \mathbb{R}$ is the confidence that $y_i$ characterizes $x_i$
	\item For classification, assume that $x_i$ belongs to $y_i$ if $r \ge $ $t(x_i)$

@@

\begin{frame}
\frametitle{\insertsection : \insertsubsection}

Assume multi-label classification problem with $q$ possible class labels $Y=\{y_1, \dots y_q\}$

Group algorithms in two categories:
\begin{itemize}
	\item \emph{Problem Transformation Methods: }Transform the learning problem into other well-established learning scenarios (fit data to algorithm philosophy)
	\item \emph{Algorithm Adaptation Methods: }Adapt popular learning techniques to deal with multi-label data directly (fit algorithm to data philosophy)
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{\insertsection : \insertsubsection}
\begin{figure}
	\begin{center}
		\includegraphics[scale = 0.75]{images/aa.png}
	\end{center}
\end{figure}
\end{frame}

\begin{frame}
\frametitle{\insertsection : \insertsubsection}
\begin{figure}
	\begin{center}
		\includegraphics[scale = 0.7]{images/pt.png}
	\end{center}
\end{figure}
\end{frame}

@@

\begin{frame}

\frametitle{\insertsection : \insertsubsection}
\textbf{Binary Relevance}
\begin{itemize}
	\item Decompose to $q$ independent binary classification problems, $h_i(x)$
	\item Cross-train on $q$ binary training sets (one for each $y_i$)
	\item Predict labels of unseen $x$ by evaluating each classifier $h_i(x)$
	\item Output labels where  $h_i(x) > 0$ else $\underset{1 \geq i \geq q}{argmax} \{h_i(x))\}$ 
\end{itemize}

Pros \& cons:
\begin{itemize}
	\item Simple, parallelizable
	\item Sensitive to class-imbalanced data
	\item Ignores label correlations (first-order method)
\end{itemize}
